Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-09 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2; Comment D2: Further details

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The natural deduction calculus proposed and used in this paper is an extension of a standard natural deduction calculus for (non-modal) higher-order logic \citep{BezmuellerBrownKohlhase} with new introduction and elimination rules for modal operators (as presented in Section \ref{sec:calculus}). This calculus is sound and complete relative to the non-modal calculus extended with Axiom K and the Necessitation rule (as demonstrated in Subsection \ref{sec:compl-sound}).

The higher-order modal natural deduction calculus proposed here has special introduction and elimination rules for modalities, as defined in Section \ref{sec:calculus}, and is sound and complete relative to an axiomatic modal calculus, as proven in Section \ref{sec:compl-sound}.

>>>>

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The natural deduction calculus proposed and used in this paper is an extension of a standard natural deduction calculus for (non-modal) higher-order logic \citep{BezmuellerBrownKohlhase} with new introduction and elimination rules for modal operators (as presented in Section \ref{sec:calculus}). This calculus is sound and complete relative to the non-modal calculus extended with Axiom K and the Necessitation rule (as demonstrated in Subsection \ref{sec:compl-sound}). There are various higher-order logics \citep{BezmuellerBrownKohlhase} and various higher-order modal logics \citep{Muskens}. The calculus proposed here can be regarded as a minimalistic calculus for a rigid higher-order modal logic K without extensionality principles. With additional axioms for stronger modal logics, such as KB and S5, this calculus is sufficient for achieving the stated aim.
